Growing Up with Nell: A Narrative Interface for Literacy

### 2012-03-12 paper.tex
Overful hboxes DIE DIE DIE.

Second, Nell seeks to grow its authoring community.  Decentralized
authorship ensures that Nell's instructional content
continues to increase its topics and
customizations.  There are no
ceilings between children and teachers: Nell
contains a story editor and everything necessary to
author and publish story modules.

To further promote collaboration,
Nell is free and open source and implemented in standard web
technologies (WebGL, HTML5, and JavaScript) with offline caching.
Resources are named by URL, even when disconnected from the
internet, which simplifies the distribution of updates to story modules and
the Nell system.  URL-based identifiers also allow third parties
to manage their own namespaces when extending Nell.

>>>>

Second, Nell seeks to grow its authoring community.  Decentralized
authorship ensures that Nell's instructional content
continues to increase in the number of topics and
customizations.  There are no
ceilings between children and teachers: Nell
contains a story editor and everything necessary to
author and publish story modules.

To further promote collaboration,
Nell is free and open source and implemented in standard web
technologies (JavaScript, HTML5, and WebGL) with offline caching.
Resources are named by URL, even when disconnected from the
internet, which simplifies the distribution of updates to story modules and
the Nell system.  URL-based identifiers also allow third parties
to manage their own namespaces when extending Nell.
